\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

Here, 2D simulations were conducted in a 5$\times$5 unit-length Hele-shaw cells (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid. Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$. Newmann (\ie no flux) boundary condition was imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions were initially imposed to the system.

Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN10} show continuous fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively. At relatively low viscosity ratio, saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed. Elongated saturation profile is due to pressure gradient near the sink region. However, in the simulation conducted with {\it VR}=10
\medskip
In fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain. Three different cases with different set-ups will follow. The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$. For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogeneous case using a mobility ratio of $10$.

>>>>

Here, 2D simulations were conducted in a 5$\times$5 cm Hele-shaw cells (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid. Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude). Newmann (\ie no flux) boundary condition was imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions were initially imposed to the system.

Figures~\ref{fig:homoheleshaw_VN3} and\ref{fig:homoheleshaw_VN10} show fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively. At relatively low viscosity ratio, saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed. Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region. However, in the simulation conducted with {\it VR}=10
\medskip
In fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain. Three different cases with different set-ups will follow. The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$. For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogeneous case using a mobility ratio of $10$.
